What if you drop that? Developmental changes in curiosity about physical interactions

### 2021-01-15 analysis/exp2_analysis.Rmd
new mturk data incorporated

# Q38-Q41 = which toy did you just drop? (catch trials)
d = d %>% # Q38 no longer exists ..
  dplyr::select(-Q11,  -Q39, -Q40, -Q41, -Q42, -Q43, -`Random ID`) %>% # -Q38,
  rename(Duration = `Duration (in seconds)`)
#write.csv(d, file="exp2_cleaned.csv")

>>>>

# Q38-Q41 = which toy did you just drop? (catch trials)
d = d %>% # Q38 no longer exists ..
  dplyr::select(-Q11, -`Q38- Catch`, -`Q39- Catch`, -`Q40- Catch`, -`Q41- Catch`, -Q42, -Q43, -`Random ID`) %>% # -Q38,
  rename(Duration = `Duration (in seconds)`)
#write.csv(d, file="exp2_cleaned.csv")

### 2021-01-15 paper/paper2021.Rmd
new mturk data incorporated

### Participants
Participants were 44 adults recruited online via Amazon Mechanical Turk who were paid $1 for their participation.

@@

```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Children online study screen configuration."}
img <- png::readPNG("figs/online-child-practice-trial.png")
grid::grid.raster(img)
```

[Sama, maybe you can explain this and the procedure in a bit more detail? (example fig if we have space)]

>>>>

### Participants
Participants were XX adults recruited online via Amazon Mechanical Turk who were paid $1 for their participation.

@@

```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=2.75, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Children online study screen configuration."}
img <- png::readPNG("figs/online-child-practice-trial.png")
grid::grid.raster(img)
```
